Effects of Trauma Life Support Training Programs on Patient Outcomes: A Pilot Cluster Randomised Trial

### 2024-08-27 pilot-publication/manuscript.Rmd
Continue to revise results and tables

The study flow diagram is shown in Figure \@ref(fig:flow-diagram) and patient sample characteristics across trial arms are shown in Table \@ref(tab:sample-characteristics). Overall, the number of females were `r females`, the median (IQR) age was `r median.age` years, and the median ISS (IQR) was `r median.iss`. A total of `r m30d` patients had the primary outcome of mortality at 30 days after arrival to the emergency department.

@@

## Feasibility Outcomes
<!--Out of X potentially eligible patients, X (X%) patients were enrolled
in the study-->. The percentage of patients who consented to follow up was `r p.consent`% and the percentage of residents who consented to training was `r recruitment.rate.residents`%. The lost to follow up rate was `r rate.lost.to.follow.up`%. The pass rate was `r pass.rate`%. The missing data rate ranged from `r min.missing.data` to `r max.missing.data`, with details for selected variables shown in Table \ref@(tab:sample-characteristics). The differences in distributions between observed and extracted data, for selected variables that were collected through observation or interview, are shown in Table \ref@(tab:observed-vs-retrospective). Overall, the data were similarly distributed, but there were considerably more missing values in extracted data compared to observed data.

@@

## Patient Participant Outcomes

After training, a total of `r m30d.standard.care` patients in the standard care arm had the primary outcome, compared to `r m30d.atls` patients in the ATLS^®^ arm and `r m30d.ptc` patients in the PTC arm. The absolute change from baseline in the primary outcome (95% CI) in the standard care arm was `r abs.change.standard.care`% units, in the ATLS^®^ arm `r abs.change.atls`% units, and in the PTC arm `r abs.change.ptc`% units. The relative change from baseline in the primary outcome (95% CI) in the standard care arm was `r rel.change.standard.care`, in the ATLS^®^ arm `r rel.change.atls`, and in the PTC arm `r rel.change.ptc`.

The absolute risk difference between the standard care and ATLS^®^ arms (95% CI) was `r arr.standard.care.atls`% units, between the standard care and PTC arms (95% CI) `r arr.standard.care.ptc`% units, and between the ATLS^®^ and PTC arms (95% CI) `r arr.atls.ptc`% units. The relative risk in the standard care arm compared with the ATLS^®^ arm (95% CI) was `r rr.standard.care.atls`, in the standard care arm compared with the PTC arm (95% CI) `r rr.standard.care.ptc`, and in the ATLS^®^ arm compared with the PTC arm (95% CI) the relative risk was `r rr.atls.ptc`. <!--The absolute and relative differences in changes from baseline comparing the three arms are shown in Supplementary materials, along with data on all secondary outcomes.-->

## Resident Participant Outcomes

A total of `r n.residents` residents were trained during this
pilot study. Overall their median confidence in managing trauma patients was `r median.confidence` (IQR `r iqr.confidence`) on a 10 point Likert scale with 10 being most confident, across trial arms and both before and after training.

>>>>

The study flow diagram is shown in Figure \@ref(fig:flow-diagram) and patient sample characteristics across trial arms are shown in Table \@ref(tab:sample-characteristics). Overall, the number of females were `r females`, the median (IQR) age was `r median.age` years, and the median ISS (IQR) was `r median.iss`. A total of `r m30d` patients died within 30 days after arrival to the emergency department.

@@

## Outcomes

<!--Out of X potentially eligible patients, X (X%) patients were enrolled
in the study-->. The percentage of patients who consented to follow up was `r p.consent`% and the percentage of residents who consented to training was `r recruitment.rate.residents`%. The lost to follow up rate was `r rate.lost.to.follow.up`%. The pass rate was `r pass.rate`%. The missing data rate ranged from `r min.missing.data` to `r max.missing.data`, with details for selected variables shown in Table \ref@(tab:sample-characteristics). The differences in distributions between observed and extracted data, for selected variables that were collected through observation or interview, are shown in Table \ref@(tab:observed-vs-retrospective). Overall, the data were similarly distributed, but there were considerably more missing values in extracted data compared to observed data.

@@

After training, a total of `r m30d.standard.care` patients in the standard care arm died within 30 days, compared to `r m30d.atls` patients in the ATLS^®^ arm and `r m30d.ptc` patients in the PTC arm. The corresponding figures for in-hospital mortality were `r inhosp.standard.care`%, `r inhosp.atls`%, and `r inhosp.ptc`%. Absolute and relative changes from baseline, as well as absolute and relative risk differences, are shown in Table \@ref(tab:outcomes). Overall, mortality was lower in the ATLS^®^ and PTC arms compared to the standard care arm. The results for all other outcomes are shown in Supplementary Materials.

```{r outcomes, echo = FALSE}
outcomes.table
```
